Learning, Evaluation and Recognition of \strips\ Action Models with Classical Planning

### 2018-04-16 doc/aij18/related_work.tex
Added input comparison table

TABLA

>>>>

\begin{table}
	\small
	\centering
	\begin{tabular}{ l | c | c | c | c | c |}
		& \multicolumn{1}{|p{2cm}|}{FO States sequences} 
		& \multicolumn{1}{|p{2cm}|}{FO Actions sequences} 
		& \multicolumn{1}{|p{2cm}|}{Plan traces (PO states)}
		& \multicolumn{1}{|p{2cm}|}{Plan traces (PO actions)}
		& \multicolumn{1}{|p{2cm}|}{Plan traces (PO both)}   \\
		\hline			
		ARMS &  & \checkmark & \checkmark & & \\
		AMAN & & & \checkmark & &\\
		LAMP & & & \checkmark & &\\
		SLAF & & & \checkmark & &\\
		LOCM & & \checkmark & & &\\
		FAMA & \checkmark & \checkmark &  \checkmark & \checkmark & \checkmark \\
	\end{tabular}
	\caption{Input comparison of main learning approaches. PO=Partial Observability, FO=Full Observability}
	\label{table:input_comparison}
\end{table}
